Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-19 ICLR25/formula.tex

Our observation (by experiments) is that \begin{align}
	I_X \approx \sum_{b\in X} I_b.
\end{align} Separately, if all nodes in $X$ are from one layer before $a$, then in experiments, we observe that

\begin{align}
	|(I_X - \sum_{b\in X} I_b)/I_X| < 1\%. \ (\text{in experiments})
\end{align} Even $X$ contains nodes from 3 layers before the target layer, in experiments, $I_X$ is still close to $\sum_{b\in X} I_b$.

@@

\begin{definition}\label{3layer}
	Suppose we have a fixed target node $a$ and a fixed source node $b$ in three layers before $a$. Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bound used in building MILP models. To compute the improvement of of upper bound of $a$ by $b$, let $v$ be the function of solutions of LP model; then we define the following function $h$ for all nodes $c$ in 2 layers before the target node $a$ as follows:
	\begin{align}
		&v_0 = v(\hat{c}), v_1 = \ReLU(v(c)), v_2 = \frac{\UB(c)v(c)-\UB(c)\LB(c)}{\UB(c)-\LB(c)}\\
		&h(c) =
		\begin{cases}
			\frac{v_0-v_1}{v_2-v_1}, & \text{if } v_2-v_1 > 0\\
			0.5, & \text{otherwise.}
		\end{cases}
	\end{align} 
\end{definition}

>>>>

Our observation (by experiments) is that \begin{align}
	I_X \approx \sum_{b\in X} I_b.
\end{align} Especially, if all nodes in $X$ are from one layer before $a$, then in experiments, we observe that

\begin{align*}
	|(I_X - \sum_{b\in X} I_b)/I_X| < 1\%. \ (\text{in experiments})
\end{align*} Even $X$ contains nodes from 3 layers before the target layer, in experiments, $I_X$ is still close to $\sum_{b\in X} I_b$.

@@

\begin{definition}\label{3layer}
	Suppose we have a fixed target node $a$ and a fixed source node $b$ in three layers before $a$. Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bounds used in building MILP models. To compute the improvement of of upper bound of $a$ by $b$, let $v$ be the function of solutions of LP model; then we define the following function $h$ for all nodes $c$ in 2 layers before the target node $a$ as follows:
	\begin{align}
		&v_0 = v(\hat{c}), v_1 = \ReLU(v(c)), v_2 = \frac{\UB(c)v(c)-\UB(c)\LB(c)}{\UB(c)-\LB(c)}\\
		&h(c) =
		\begin{cases}
			\frac{v_0-v_1}{v_2-v_1}, & \text{if } v_2-v_1 > 0\\
			0.5, & \text{otherwise.}
		\end{cases}
	\end{align} 
\end{definition}
